\acknowledgements{
I must take this opportunity to thank all the support received during my PhD journey, without which this thesis could not have been possible. 

First of all, I would like to express my greatest appreciation to my PhD supervisors, Professor Geoff V. Merrett and Dr. Alex S. Weddell. 
They are the role models of my life. 
Not only did they guide me how to conduct research, but more importantly, they demonstrated a way of thinking and behaving. 
Their supervision is the invaluable fortune in my life.

Next, I would like to thank the University of Southampton and Xiamen University for offering a PhD opportunity and waiving tuition fees. 
I also sincerely appreciate the China Scholarship Council for the 4-year scholarship that covered my living costs during the PhD study. 
I feel very fortunate that I received the opportunity and financial support, and never take it for granted.

It is also a huge pleasure to meet the people in the Cyber Physical Systems research group, where I have learnt and enjoyed very much from our conversations and technical discussions. 
It is impossible to name all of them, but I will make my poorest attempt to thank: Domenico, Oktay, Sivert, Theo, Alberto, Edward, Samuel Wong, Samuel Isuwa, Charan, Amin, Lei, Tasios, Tim, Sara, Jia, Chenyang, and Runshan. 
I also cherish those lovely friends in Southampton --- we shared the beautiful moments and encouragement. 

Finally, I want to express my deepest love to my parents, GUO Xuan and ZHAN Shushao, and my girlfriend, HUANG Yuen. 
Though we were physically apart for most of the time in the past four years, you have always been connecting with me regularly and supporting me throughout the hardest periods. 

Life has to go on, and I am on the way. Best wishes to all the people and take care!
}